### 2016-02-20 abstract.tex
abstract intro changes

Measuring the distance between two program executions is a fundamental problem in dynamic analysis of software, and used in many proposed testing and debugging algorithms.  This paper proposes a novel metric for measuring distance between executions, and specializes it to the most commonly needed case, failing test cases.  The metric is based on a causal concept of distance: executions are similar to the degree that changes in the program itself, introduced using mutation operators, cause similar changes in the correctness of the executions.  Specifically, if two failing test cases (for the original program) become successful due to the same mutant, they are more likely to be due to the same fault.  This metric both improves an existing method for identifying test cases failing due to unique faults and enables novel fault localization approaches.  We evaluate our methods using more than 50 faults and 2,500 test cases for two complex, widely-used, real-world compilers, and demonstrate improvements over state-of-the-art methods.

>>>>

Measuring the distance between two program executions is a fundamental problem in dynamic analysis of software, and useful in many test generation and debugging algorithms.  This paper proposes a novel metric for measuring distance between executions, and specializes it to the most commonly needed case, failing test cases.  The metric is based on a causal concept of distance: executions are similar to the degree that changes in the program itself, introduced using mutation operators, cause similar changes in the correctness of the executions.  Specifically, if two failing test cases (for the original program) become successful due to the same mutant, they are more likely to be due to the same fault.  This metric both improves an existing method for identifying test cases failing due to unique faults and enables novel fault localization approaches.  We evaluate our methods using more than 50 faults and 2,500 test cases for two complex, widely-used, real-world compilers, and demonstrate improvements over state-of-the-art methods.

### 2016-02-20 introduction.tex
abstract intro changes

Recent advances in automated test generation, reported in numerous papers and implemented in powerful tools \cite{csmith,jsfunfuzz,ISSTA12,LangFuzz,ZhendongPLDI,ZhendongOOPSLA}, have made it easier to find subtle faults in compilers.  Unfortunately, the blessing of many failing test cases can quickly become a curse for a compiler developer.  Simply discovering which test cases in a large set of failures represent distinct faults (and possibly already known faults) is a very difficult problem \cite{PLDI13,Podgurski04}.  For simple crashes and assertion violations, bucketing failures is sometimes easy.  When a failure is detected by differential testing \cite{Differential}, where two compilers or optimization levels disagree, the problem is so hard that it may turn potential users away from automated test generation \cite{PLDI13}.  Even once a fault is identified, fixing the problem can be very difficult.  There is reason to suspect, due to complexity of intermediate representation, interaction of a very large number of optimizations, subtle aspects of language semantics, and other issues, that debugging compiler faults may usually be harder than debugging faults in other kinds of software (this is probably not limited to compilers; debugging systems software in general is hard \cite{mickens}).
We propose the use of mutants \cite{mutant}, small syntactic changes to source code, to address some of the problems of debugging based on large sets of automatically generated test cases.  The underlying idea is that if two failures can be repaired in the same way, even if that repair only avoids the failure and does not truly fix it, they are likely due to the same fault. Repairs can also provide  information for understanding and debugging discovered faults. This approach also suggests a possible metric for comparing any two program executions, not just failing test cases.

>>>>

Recent advances in automated test generation, reported in numerous papers and implemented in powerful tools \cite{csmith,jsfunfuzz,ISSTA12,LangFuzz,ZhendongPLDI,ZhendongOOPSLA}, have made it easier to find subtle faults in, e.g., modern optimizing compilers.  Unfortunately, the blessing of many failing test cases can quickly become a curse for a compiler developer.  Simply discovering which test cases in a large set of failures represent distinct faults (and possibly already known faults) is a very difficult problem \cite{PLDI13,Podgurski04}.  For simple crashes and assertion violations, bucketing failures is sometimes easy.  When a failure is detected by differential testing \cite{Differential}, where two compilers or optimization levels disagree, the problem is so hard that it may turn potential users away from automated test generation \cite{PLDI13}.  Even once a fault is identified, fixing the problem can be very difficult.  There is reason to suspect, due to complexity of intermediate representation, interaction of a very large number of optimizations, subtle aspects of language semantics, and other issues, that debugging compiler faults may usually be harder than debugging faults in other kinds of software (this is probably not limited to compilers; debugging systems software in general is hard \cite{mickens}).
We propose the use of mutants \cite{mutant}, small syntactic changes to source code, to address some of the problems of debugging based on large sets of automatically generated test cases.  The underlying idea is that if two failures can be repaired in the same way, even if that repair only avoids the failure and does not truly fix it, they are likely due to the same fault. Repairs can also provide  information for understanding and debugging discovered faults. This approach also suggests a possible metric for comparing any two program executions, not just failing test cases.
